A novel route to the spontaneous formation of porous crystals via viscoelastic phase separation

### 2016-06-20 crystal-gel/talk_Roscoff.tex
backslides

\usepackage{siunitx}

@@

>>>>

\usepackage[separate-uncertainty = true]{siunitx}

@@

\begin{frame}{Reproducibility in capillary}
\hfill $\phi\approx 0.33$, $c_P=\SI{0.40}{\milli\gram/\gram}$

\includegraphics[width=\textwidth]{nature/capillary}
\end{frame}

\begin{frame}{Transition probabilities}
\vspace{\baselineskip}
\includegraphics[width=\textwidth]{nature/sfig1.pdf}
\end{frame}

\begin{frame}{Evolution local volume fraction}
\vspace{\baselineskip}
12-neighboured particles
\begin{center}
\includegraphics{nature/local_phi12.pdf}
\end{center}
\end{frame}

\begin{frame}{phase definition}
\begin{description}
\item[crystal]
	\begin{itemize} 
	\item particle $i$ has $N_b(i)=12$ neighbours
	\item $\displaystyle q_{6 m}(i)=\frac{1}{N_b(i)}\sum_{j=1}^{N_b(i)}
Y_{6 m}(\mathbf{r_{ij}}),\quad -6 <m<6$
	\item crystalline bond $(i,j)$: \[(\mathbf{q}_{6}(i)/|\mathbf{q}_{6}(i)|)\cdot(\mathbf{q}_{6}(j)/|\mathbf{q}_{6}(j)|)>0.7\]
	\item crystalline particle: $7$ crystalline bonds
	\end{itemize}
\item[surface] two neighbouring crystal particles
\item[liquid] at least four neighbouring particles
\item[gas]
\end{description}
\end{frame}

\begin{frame}{Colloid and polymer sizes}
Direct measurement \alert{too imprecise}
\begin{itemize}
\item diffusion constant $\Rightarrow R= \SI{2.3 +- 0.05}{\micro\metre}$
\item Flory scaling litterature measurements $\Rightarrow R_g=\SI{76. +- 50.}{\nano\metre}$
\end{itemize}

\begin{block}{Adjusting theoretical and experimental phase diagrams}
\begin{enumerate}
\item to have the final local volume fraction of the 12-neighboured particles in the crystallising sample to be equal to the theoretical equilibrium crystal volume fraction 
\item to have the theoretical spinodal line to correspond to the gel region boundary.
\end{enumerate}
\end{block}
Starting from our initial estimates of $\sigma$ and $R$ we iteratively converge to $R=\SI{80}{\nano\metre}$, $\sigma = \SI{2.25}{\micro\metre}$ and a crystal (without defects) at $0.723$.
\end{frame}
